minutes of meetings

### 2021-03-08 note/minutes.Rmd
more on the targeted testing, minutes are updated

>>>>

### Date: MArch 8
 - There are papers by Friston 
 Friston, Karl J., Thomas Parr, Peter Zeidman, Adeel Razi, Guillaume Flandin, Jean Daunizeau, Oliver J. Hulme, et al. “Dynamic Causal Modelling of COVID-19.” ArXiv:2004.04463 [q-Bio], April 9, 2020. http://arxiv.org/abs/2004.04463.

 - in there model, they have a fig1 big model includes testing, don't know how they have testing based on symptoms (it seems), the thetas here represent just parameters , sigma is sigmoid function (we think), the 4 compartment ...
